Toxic code snippets on Stack Overflow

### 2017-10-14 cloverflow-tse/cloverflow.tex
Completed the whole paper (RQ1 - RQ5).

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{itemize}
	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
		code cloned between Stack Overflow and open source projects?} We
	quantitatively measured the number of online code clones between Stack
	Overflow and open source projects to understand the scale of the
	problem. 
	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
		code clones occur?} We categorised online clones into seven
	categories allowing insights to why online code clones are created.
	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
		online code clones up-to-date compared to their counterparts in the
		original projects?} We were interested in the outdated Stack
	Overflow code examples since users are potentially reusing
	them. 
	\item \textbf{RQ4 (Software licensing violation): }\textit{Do
		licensing conflicts occur between Stack Overflow clones and their
		originals?} We investigated whether the reuse of online code clones
	can cause software developers to violate licenses.
	\item \textbf{RQ5 (Developers' awareness): }\textit{Do Stack Overflow
		users aware of the outdated code and licensing problem when
		they answer a question on Stack Overflow?} 
	We surveyed 607 high reputation Stack Overflow users to study their
	awareness of the issues.
\end{itemize}

@@

\begin{table}
	\centering
	\caption{The two groups of Stack Overflow users invited to take the survey}
	\label{tab:survey_target}
	\begin{tabular}{lrrrr}
		\toprule
		Target group & Reputation & Sent emails & Answers & Rate \\
		\midrule
		Group 1 & 963,731--7,674 & 300 & 112 & 37\% \\
		Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

The participants were invited to take the survey via email addresses on their
public Stack Overflow and GitHub profiles. We selected the answerers who had highly
ranked all-time reputations\footnote{Stack Overflow Users (data as of 25 July
	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}} and
separated them into two groups (see \Cref{tab:survey_target}) so that we can
compare the results or observe similar patterns between them. 
The first group had reputation from 963,731 (the
highest) to 7,674, and the second group had reputation from 7,636 to 6,999 which
we sent out 300 and 307 emails (excluding undelivered ones) respectively. The
survey was open for participation for two months, from 25 August 2017 to 25 August
2017, before we collected and analysed the responses.

@@

\subsection{RQ1: Online Code Clones}

@@

\subsection{RQ2: Patterns of Online Code Cloning}

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	\resizebox{\linewidth}{!}{
		\begin{tabular}{cc|lcp{4cm}@{}rrc|lc@{}c}
			\toprule
			\multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{3}{c}{Changes} \\ 
			\midrule
			Post & Date & Project & Ver. & File & Start & End & Date & Issue ID & Type$^*$ & Date \\
			\midrule
			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & & Bug 439874 & \textit{S} & 17-Mar-15 \\
			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & HADOOP-11323 & \textit{S} & 20-Nov-14 \\
			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & HHH-10458 & \textit{S} & 5-Feb-16 \\
			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & & LUCENE-4095 & \textit{D} & 31-May-12 \\
			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & BZ 59823 &\textit{R} & 4-Aug-16 \\
			12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 49 & 60 & 7-Dec-09 & 57593 & \textit{R} & 30-Apr-15 \\
			8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & N/A & \textit{D} & 20-May-11 \\
			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotation\newline HandlerMapping.java & 78 & 92 & 20-Oct-10 & SPR-14129 & \textit{D} & 20-Jan-12 \\
			14019840 & 24-Dec-12 & struts & 2.2.1 & DefaultActionMapper.java & 273 & 288 & & WW-4225 & \textit{S} & 18-Oct-13 \\
			\bottomrule 
			\multicolumn{10}{l}{{\footnotesize * \textit{S}:
					modified/added/deleted statements, \textit{D}: file
					has been deleted,  \textit{R}: method has been
					rewritten completely}}
		\end{tabular} %
	}
\end{table*}

@@

\subsection{RQ3: Outdated Online Code Clones}

@@

\subsection{RQ4: Software Licensing Violation}

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.2cm}lrrr}
			\toprule
			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
			\midrule
			Compatible & Apache-2 & Apache-2 & 1 & & \\
								  & EPLv1 & EPLv1 & 2 & & \\
								  & No license & No license	& 20 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 23 & & \\
			\midrule
			Incompat. & No license & EPLv1	& 10 & & \\
								& No license & GPLv2/2+/3+	& 7 & & \\
								& No license & AGPLv3 & 1 & & \\
								& No license & Apache-2 & 46 & & \\
								& No license & BSD/BSD3	& 4 & & \\
								& No license & LesserGPL/v2.1+/v3+ & 17 & & \\
								& spdxBSD3 & LesserGPLv2.1+	& 1 & & \\
			\midrule
			\multicolumn{3}{l}{Total} & 86 & & \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

%If developers copy and reuse these licensed pieces of code in their projects,
% conflicts may happen without their realisation.
In our study, we reveal another type of toxic code snippets which is software
licensing issues caused by code cloned to Stack Overflow. We found evidence that
154 pieces of code have been copied from Qualitas projects to Stack Overflow as
examples. Their status of accepted answers increase their chances of being
reused. Even though most of the Qualitas projects came with a software license,
we found that the license information were frequently missing after the code was
copied to Stack Overflow. The licensing terms on top of source code files are
not copied because usually only a small part of the file was cloned. In overall,
we can see that most of the Stack Overflow snippets do not contain licensing
terms while their clone counterparts in Qualitas projects do. 
Pleaste note that the
results here are analysed at file level, not clone fragment, thus there are some
clone pairs that share the same result and we combine them into a single pair.
The summary of
licensing information is listed in \Cref{tab:license_abc}.

\textbf{Compatible license:} There are 40 pairs which have compatible
licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
	License v.1 (EPLv1)}; or a pair of no license vs.~\emph{Creative
	Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
	BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
code and text on Stack Overflow are
protected by \emph{CC BY-NC-SA 3.0}
, we can treat the Stack Overflow code snippets
without licensing information as having \emph{CC BY-NC-SA 3.0} by
default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
requests an attribution when reused.

\textbf{Incompatible license:} there are 358 clone pairs which do not
contain licensing information after they are posted on Stack Overflow
or contain a different license from their Qualitas clone
counterparts. More than half (79) of \textbf{QS} clone pairs have
their licensing terms removed or changed when posted on Stack
Overflow. For \textbf{EX} clone pairs, we searched for licensing terms of the
original source code from the external sources. We found that 77 out
of 88 EX clone pairs have incompatible licenses.
%They are clones that have been identified to be copied from an external source.
Similarly, the license statement was removed from Stack Overflow
snippets. Of 226 \textbf{UD} clone pairs, 202 pairs have incompatible
licenses. Again, most clones in Qualitas contain a license
while the Stack Overflow snippets do not.
%
%\Cref{fig:sankey_license} shows the direction of changes in online code clone license. The direction of the change is from left to right. The thickness of the line reflects the number of clones for that relationship. In \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online clones have their licenses changed from having a license to ``No license'' on Stack Overflow. The same findings were found for EX online clones as depicted in \Cref{fig:sankey_license} (B). We found that most of the EX clones have their licensing information stripped of after copying to Stack Overflow. These clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack Overflow which is strongly permissive. These used-to-be-licensed code are dangerous for being reused because they can implicitly conflict with the reused software's license.

\textbf{For RQ4, we found 358 code snippets on Stack Overflow that
	violate the license of their original software. The majority of them
	do not contain licensing statements after they have been copied to
	Stack Overflow.}

@@

We received 112 answers (37\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}\cite{Punter2003}.
We only present a summary of the survey answers in this paper. The full analysis
is available as a technical report \FIXME{Ok?}.

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_exp_1-crop}
		\caption{Group 1}
		\label{fig:survey_group1_exp}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.62\linewidth]{survey_exp_2-crop}
		\caption{Group 2}
		\label{fig:survey_group2_exp}
	\end{subfigure}
	\caption{Experience of the Stack Overflow users}
	\label{fig:survey_exp}
\end{figure}

\subsubsection{Answerers' Experience}
The majority of users in both groups are experienced developers 
with more than 10 years of experience or between 5 to 10 years 
as depicted in \Cref{fig:survey_exp}. They are active users and
regularly answer questions on Stack Overflow.
Eighty one and sixty percent of users from Group 1 and Group 2 
answer questions at least once a week.

\begin{figure*}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_snippet_source_1}
		\caption{Group 1}
		\label{fig:survey_snippet_source_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_snippet_source_2}
		\caption{Group 2}
		\label{fig:survey_snippet_source_2}
	\end{subfigure}
	\caption{Sources of code snippets in Stack Overflow answers}
	\label{fig:survey_snippet_source}
\end{figure*}

\subsubsection{Code Snippets in Answers} 
A large amount of 91 (81\%) and 58
(68\%) users in both group include code snippets in more than sixty percent of
their answers. \Cref{fig:survey_snippet_source} explains where are these code
snippets from. Stack Overflow answerers mostly write new code from scratch 
or modify from the code snippets in question for each answer, while 
fewer numbers are from other sources including their personal projects, 
their company projects, open source projects. We found 27 answerers in both Group 1
and Group 2 occasionally to very frequently copy code from open source projects.

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_1}
		\caption{Group 1}
		\label{fig:survey_license_1}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_2}
		\caption{Group 2}
		\label{fig:survey_license_2}
	\end{subfigure}
	\caption{Software license in Stack Overflow code snippets.}
	\label{fig:survey_license}
\end{figure}

\subsubsection{Outdated Code Snippets}

We found that 63.1\% of Stack Overflow answerers in Group 1 have been notified of
outdated code in their answers (see \Cref{fig:survey_outdated}). The ratio drops to 47.6\% in
Group 2. Thus, at least roughly half of the top answerers on Stack Overflow
are aware of their outdated code in some of their answers.

\begin{figure}
	\centering
	\includegraphics[width=.8\linewidth]{survey_outdated}
	\caption{Percentage of answerers who are notified of outdated code in their Stack Overflow answers.}
	\label{fig:survey_outdated}
\end{figure}%

We then asked the participants to have been notified of their outdated code
(80 and 48 participants from Group 1 and 2 respectively) a
follow-up questions ``how frequently did you fix your outdated code on Stack
Overflow?''. The answers, depicted in \Cref{fig:survey_outdated_fix}, show that
more than half of them frequently fix the outdated code snippets. However, there
are 18.8\% of the answerers in both groups who rarely or never fix their code.

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{survey_outdated_fix_1}
		\caption{Group 1}
		\label{fig:survey_outdated_fix_1}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{survey_outdated_fix_2}
		\caption{Group 2}
		\label{fig:survey_outdated_fix_2}
	\end{subfigure}
	\caption{Frequency of the answerers fixing their outdated code.}
	\label{fig:survey_outdated_fix}
\end{figure}

The answers support our findings of outdated online code clones. Although most
of the Stack Overflow answerers know that their code are outdated, the code may
still not be fixed.

\subsubsection{License of Code Snippets} 
More than half of the answerers in both groups (63.1\% and 61.9\% respectively)
are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0
Unported (CC BY-SA 3.0) to content in the posts, including code snippets, while
the rest of 36.9\% and 38.1\% are not. Nevertheless, we found that almost all 
of them do not include license statement in their code snippets (as depicted in
\Cref{fig:survey_license}) due to several reasons. First, some answerers chose to 
post only their own code or code that was adapted from the question, hence
 they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
company or open source projects that they knew were permitted to be publicly distributed.
Third, some answerers believe that code snippets in their answers are too small 
to claim any intellectual property on them and fall under fair use~\cite{fairuse}.

While nobody explicitly includes a software license in their snippets,
many users include a statement on their profile page that states all their
answers are under a certain license. For example, \textit{All code posted by me on
Stack Overflow should be considered public domain without copyright. For
countries where public domain is not applicable, I hereby grant everyone the
right to modify, use and redistribute any code posted by me on Stack Overflow
for any purpose. It is provided "as-is" without warranty of any kind.}  Many
users either declare their snippets to be public domain, or they grant
additional licenses, e.g. Apache 2.0 or MIT/Expat.

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{survey_license_check_1}
		\caption{Group 1}
		\label{fig:survey_license_check_1}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=\linewidth]{survey_license_check_2}
		\caption{Group 2}
		\label{fig:survey_license_check_2}
	\end{subfigure}
	\caption{Frequency of the answerers checking license of their code snippets against Stack Overflow's CC BY-SA 3.0.}
	\label{fig:survey_license_check}
\end{figure}

We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0. As shown in \Cref{fig:survey_license_check}, approximately 69\% of answerers from both groups did not perform the checking. Nonetheless, they are about 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.

\subsubsection{Open Comments} 
We also invited the participants to give any comments regarding answering Stack Overflow with code snippets. These are some interesting comments we received.

Comment 1: ``The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software "professionals" that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.  A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about. Think php/mysql tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}). They're also full of toxic code snippets.''

Comment 2: ``When I copy code it's usually short enough to be considered "fair use" but I am not a lawyer or copyright expert so some guidance from SO would be helpful. I'd also like the ability to flag/review questions that violate these guidelines.''

>>>>

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{itemize}
	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
		code cloned between Stack Overflow and open source projects?} We
	quantitatively measured the number of online code clones between Stack
	Overflow and open source projects to understand the scale of the
	problem. 
	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
		code clones occur?} We categorised online clones into seven
	categories allowing insights to why online code clones are created.
	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
		online code clones up-to-date compared to their counterparts in the
		original projects?} We were interested in the outdated Stack
	Overflow code examples since users are potentially reusing
	them. 
	\item \textbf{RQ4 (Software licensing violation): }\textit{Do
		licensing conflicts occur between Stack Overflow clones and their
		originals?} We investigated whether the reuse of online code clones
	can cause software developers to violate licenses.
	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }
		\subitem \textit{RQ5.1 Do Stack Overflow
		answerers aware of the outdated code when
		they answer a question on Stack Overflow?} 
		\subitem \textit{RQ5.2 Do Stack Overflow
			answerers aware of licensing conflicts when
			they answer a question on Stack Overflow?}

	We surveyed 607 high reputation Stack Overflow users to study their
	awareness of the two issues.
\end{itemize}

@@

@@

The participants were invited to take the survey via email addresses on their
public Stack Overflow and GitHub profiles. We selected the answerers who had highly
ranked all-time reputations\footnote{Stack Overflow Users (data as of 25 July
	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}.
They had a reputation from 963,731 (the
highest) to 6,999 which
we sent out 607 emails (excluding undelivered ones) respectively. The
survey was open for participation for two months, from 25 July to 25 September
2017, before we collected and analysed the responses.

@@

\subsection{RQ1: Online Code Clones} 
\vspace{0.25cm}
\textit{To what extent is source
	code cloned between Stack Overflow and open source projects?}
\vspace{0.25cm}

@@

\subsection{RQ2: Patterns of Online Code Cloning}
\vspace{0.25cm}
\textit{Why do online code clones occur?}
\vspace{0.25cm}

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	\resizebox{\linewidth}{!}{
		\begin{tabular}{cc|lcp{4cm}@{}rrc|lc@{}c}
			\toprule
			\multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{3}{c}{Changes} \\ 
			\midrule
			Post & Date & Project & Ver. & File & Start & End & Date & Issue ID & Type$^*$ & Date \\
			\midrule
			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & Bug 439874 & \textit{S} & 17-Mar-15 \\
			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & HADOOP-11323 & \textit{S} & 20-Nov-14 \\
			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & HHH-10458 & \textit{S} & 5-Feb-16 \\
			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & 31-Mar-10 & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & 6-Apr-13 & LUCENE-4095 & \textit{D} & 31-May-12 \\
			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & BZ 59823 &\textit{R} & 4-Aug-16 \\
			12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 49 & 60 & 7-Dec-09 & 57593 & \textit{R} & 30-Apr-15 \\
			8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & N/A & \textit{D} & 20-May-11 \\
			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotation\newline HandlerMapping.java & 78 & 92 & 20-Oct-10 & SPR-14129 & \textit{D} & 20-Jan-12 \\
			14019840 & 24-Dec-12 & struts & 2.2.1 & DefaultActionMapper.java & 273 & 288 & 17-Jul-10 & WW-4225 & \textit{S} & 18-Oct-13 \\
			\bottomrule 
			\multicolumn{10}{l}{{\footnotesize * \textit{S}:
					modified/added/deleted statements, \textit{D}: file
					has been deleted,  \textit{R}: method has been
					rewritten completely}}
		\end{tabular} %
	}
\end{table*}

@@

\subsection{RQ3: Outdated Online Code Clones}
\vspace{0.25cm}
\textit{Are online code clones up-to-date compared to their counterparts in the original projects?}
\vspace{0.25cm}

@@

\subsection{RQ4: Software Licensing Violation}
\vspace{0.25cm}
\textit{Do
	licensing conflicts occur between Stack Overflow clones and their
	originals?}
\vspace{0.25cm}

\begin{table}
	\centering
	\caption{License mapping of online clones (file-level)}
	\label{tab:license_abc}
	%\small
	\resizebox{\linewidth}{!}{
		\begin{tabular}{lp{2.5cm}p{2.5cm}rrr}
			\toprule
			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
			\midrule
			Compatible 
			& Apache-2 & Apache-2 & 1 & & \\ 
			& EPLv1 & EPLv1 & 2 & & 1 \\ 
			& Proprietary & Proprietary & & 2 & \\ 
			& Sun Microsystems & Sun Microsystems & & 3 & \\ 
			& No license & No license & 20 & 9 & 2 \\ 
			& CC BY-SA 3.0 & No license & & 1 & \\
			\midrule
			\multicolumn{3}{l}{Total} & 23 & 15 & 3 \\
			\midrule
			Incompat. 
			& No license & AGPLv3/3+ & 1 & & 4 \\
			& No license & Apache-2 & 46 & 14 & 12 \\  
			& No license & BSD/BSD3 & 4 & & 1 \\ 
			& No license & CDDL or GPLv2 & & & 6 \\ 
			& No license & EPLv1 & 10 & & 6 \\
			& No license & GPL/v2/2+/3+ & 8 & 48 & 7 \\ 
			& No license & LesserGPL/v2.1+/3+ & 16 & & 9 \\ 			
			& No license & MPLv1.1 & & & 1 \\ 
			& No license & Oracle & & 3 \\ 
			& No license & Proprietary & & 1 & 2 \\ 
			& No license & Sun Microsystems & & 1 & 2 \\ 
			& No license & Unknown & & 11 & \\
			& New BSD3 & LesserGPLv2.1+ & 1 & & \\ 
			\midrule
			\multicolumn{3}{l}{Total} & 86 & 78 & 50 \\
			\bottomrule
		\end{tabular} 
	}
\end{table}

%If developers copy and reuse these licensed pieces of code in their projects,
% conflicts may happen without their realisation.
In our study, we reveal another type of toxic code snippets which is software
licensing issues caused by code cloned to Stack Overflow. We found evidence that
154 pieces of code have been copied from Qualitas projects to Stack Overflow as
examples. Another 111 pieces of code are cloned from external sources. Their
status of accepted answers increase their chances of being reused. Even though
most of the Qualitas projects came with a software license, we found that the
license information were frequently missing after the code was copied to Stack
Overflow. The licensing terms on top of source code files are not copied because
usually only a small part of the file was cloned. In overall, we can see that
most of the Stack Overflow snippets do not contain licensing terms while their
clone counterparts in Qualitas projects and external sources do. Since licensing
statement resides on top of a file, the results here are analysed at file level,
not clone fragment, and clone pairs from the same file are merged. 
The summary of licensing information is listed in
\Cref{tab:license_abc}.

\textbf{Compatible license:} There are 41 pairs which have compatible
licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
	License v.1 (EPLv1)}; or a pair of \emph{Creative
	Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
	BY-NC-SA 3.0)} vs.~no license. These clones are safe for being reused. Since source
code and text on Stack Overflow are
protected by \emph{CC BY-NC-SA 3.0}
, we can treat the Stack Overflow code snippets
without licensing information as having \emph{CC BY-NC-SA 3.0} by
default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
requests an attribution when reused.

\textbf{Incompatible license:} there are 214 clone pairs which do not contain
licensing information after they are posted on Stack Overflow or contain a
different license from their Qualitas clone counterparts. Almost all (85) of
\textbf{QS} clone pairs have their licensing terms removed or changed when
posted on Stack Overflow. One QS clone pair posted by a JFreeChart developer
changes its license from Lesser GPL v2.1+ to New BSD 3-clause. The JFreeChart
developer may intentionally change the license to be more suitable for Stack
Overflow since New BSD 3-clause license allows reuse without requiring the same
license in the distributing software or statement of changes.

For \textbf{EX}
clone pairs, we searched for licensing terms of the original source code from
the external sources. We found that 78 out of 93 EX clone pairs have
incompatible licenses. %They are clones that have been identified to be copied
% from an external source.
Similarly, the license statement was removed from Stack Overflow snippets.

Of 53 \textbf{UD} clone pairs, 50 pairs have incompatible licenses. Again, most
clones in Qualitas contain a license while the Stack Overflow snippets do not.
%
%\Cref{fig:sankey_license} shows the direction of changes in online code clone
% license. The direction of the change is from left to right. The thickness of
% the line reflects the number of clones for that relationship. In
% \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online
% clones have their licenses changed from having a license to ``No license'' on
% Stack Overflow. The same findings were found for EX online clones as depicted
% in \Cref{fig:sankey_license} (B). We found that most of the EX clones have
% their licensing information stripped of after copying to Stack Overflow. These
% clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack
% Overflow which is strongly permissive. These used-to-be-licensed code are
% dangerous for being reused because they can implicitly conflict with the
% reused software's license.

\textbf{For RQ4, we found 214 code snippets on Stack Overflow that
	violate the license of their original software. The majority of them
	do not contain licensing statements after they have been copied to
	Stack Overflow.}

@@

\begin{table}
	\centering
	\caption{Stack Overflow answerers taken the survey}
	\label{tab:survey_target}
	\begin{tabular}{rrrr}
		\toprule
		Reputation & Sent emails & Answers & Rate \\
		\midrule
		963,731--6,999 & 607 & 201 & 33\% \\
		\bottomrule
	\end{tabular}
\end{table}

We received 201 answers (33\% response rate) from 607 emails we sent to the
Stack Overflow answerers. The response rate was high
considered other online survey in software engineering that received
approximately 14--20\%~\FIXME{double-check the citation again for the magic
	numbers.}\cite{Punter2003}.
We only present a summary of the survey answers in
this paper and the full analysis is available as a technical report \FIXME{add URL}.

\subsubsection{General Information}
As shown in \Cref{tab:survey_exp}, majority of the answerers are experienced
developers with more than 10 years of experience (55.4\%) or between 5 to 10
years (28.7\%). They are active users and regularly answer questions. 49
participants answer questions on Stack Overflow every day.

\begin{table}
	\centering
	\caption{Experience of Stack Overflow answerers}
	\label{tab:survey_exp}
	\begin{tabular}{lrr}
		\toprule
		Experience & Amount & Percent \\
		\midrule
		Less than a year & 1 & 0.5\% \\
		1 -- 2 years & 1 & 0.5\% \\
		3 -- 5 years & 30 & 14.9\% \\
		5 -- 10 years & 58 & 28.9\% \\
		More than 10 years	& 111 & 55.2\% \\
		\bottomrule
	\end{tabular}
\end{table}

\subsubsection{Code Snippets in Answers}

\begin{table}
	\centering
	\caption{Frequency of including code snippets in answers}
	\label{tab:survey_code_snippet_frequency}
	\begin{tabular}{lrr}
		\toprule
		Include code snippets & Amount & Percent \\
		\midrule
		Very Frequently (81--100\% of the time)	& 84 & 42\% \\
		Frequently (61--80\% of the time) &	63 & 31\% \\
		Occasionally (41--60\% of the time) & 40 & 20\% \\
		Rarely (21--40\% of the time) & 11 & 6\% \\
		Very Rarely (1--20\% of the time) & 2 & 1\% \\
		Never (0\% of the time) & 1 & 1\% \\
		\midrule
		Total & 201 & 100\% \\
		\bottomrule
	\end{tabular}
\end{table}

84 and 63 answerers include code snippets in more than 80\% and 60\% of
their answers respectively. Interestingly, there is one answerer who never
include code snippet in his/her answers.

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{survey_snippet_source}
	\caption{The sources of code snippets in Stack Overflow answers}
	\label{fig:survey_snippet_source}
\end{figure}

We asked the participants for the origins of code snippets in their answers. We
provided six locations (allow multiple selection) including the answerer's
personal projects, the answerer's company projects, open source projects,
writing the code from scratch, copying and modifying the code from the question,
and others (e.g.~code that are copied from other questions or answers on Stack
Overflow) and asked them to rate how often they copied the code from these
locations. The results are shown in \Cref{fig:survey_snippet_source}. Looking at
Very Frequently section, we can see that the answerers mainly write new code
from scratch (71) or modify from the code snippets in question for each answer
(56), while fewer numbers are from other sources including their personal
projects (42), their company projects (10), and open source projects (14).
Although copying from open source projects is not the most popular choice, the answerers
still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
participants who frequently, occasionally, and rarely copied code snippets from open
source projects.

\subsubsection{Outdated Code Snippets} 
\vspace{0.25cm}
\textit{Do Stack Overflow
	answerers aware of the outdated code when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}

We asked the answerers if they have ever been notified about outdated code in
their answers. 111 participants selected \textit{Yes} while the other 89 participants
selected \textit{No}. However, we found inconsistent results when we asked a follow up
question on the frequency of being notified. As displayed in
\Cref{tab:survey_code_snippet_outdated}, the number of participants who has
\textit{Never} been notified about outdated code snippets in their answers drops
from 89 to 69.

\begin{table}
	\centering
	\caption{Awareness to outdated code snippets in answers}
	\label{tab:survey_code_snippet_outdated}
	\begin{tabular}{lrr}
		\toprule
		Notified of outdated code & Amount & Percent \\
		\midrule
		Very frequently (81--100\% of my answers) & 2 & 1\% \\
		Frequently (61--80\% of my answers) & 1 & 0.5\% \\
		Occasionally (41--60\% of my answers) & 9 & 4.5\% \\
		Rarely (21--40\% of my answers) & 16 & 8\% \\
		Very rarely (1--20\% of my answers) & 103 & 51.5\% \\
		Never (0\% of my answers) & 69 & 34.5\% \\
		\midrule
		Total & 200 & 100\% \\
		\bottomrule
	\end{tabular}
\end{table}

We found that although the answerer have been notified of
outdated code in their answers, 51.5\% occurs very rarely (only 1--20\% of the answers). 
Only 3 participants reported that they were notified in more than 60\% of their answers.

\begin{table}
	\centering
	\caption{Fixing of outdated code snippets in answers}
	\label{tab:survey_code_snippet_outdated_fix}
	\begin{tabular}{lrr}
		\toprule
		Fixing of outdated code & Amount & Percent \\
		\midrule
		Very frequently (81--100\% of the cases) & 48 & 36.6\% \\
		Frequently (61--80\% of the cases) & 27 & 20.6\% \\
		Occasionally (41--60\% of the cases) & 30 & 22.9\% \\
		Rarely (21--40\% of the cases) & 11 & 8.4\% \\
		Very rarely (1--20\% of the cases) & 8 & 6.1\% \\
		Never (0\% of the cases) & 7 & 5.3\% \\
		\midrule
		Total & 131 & 100.0\% \\
		\bottomrule
	\end{tabular}
\end{table}

We then asked 131 participants to have been notified of their outdated code a
follow-up questions ``how frequently did you fix your outdated code on Stack
Overflow?''. The answers, depicted in
\Cref{tab:survey_code_snippet_outdated_fix}, show that more than half of them
(57.2\%) very frequently or frequently fix the outdated code snippets. However,
there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
their outdated code.

\textbf{To answer RQ 5.1, although most of the Stack Overflow answerers are aware that their code
can be outdated. 51.5\% of the answerers were very rarely notified while 35.5\% never been notified of
outdated code in the answers. 19.8\% of them rarely fix the outdated code or left them unfixed.}

The responses from the answerers support our findings of outdated online code
clones. In addition, this
results only reflect experienced answerers who accumulate the reputation for a
long time. Due to the voting mechanism of Stack Overflow, high reputation users
usually provide quality answers and earn up votes from other users. They must be
very careful when posting code snippets in the answer to avoid problems and, in
the end, getting down votes. It is also interesting to compare the findings to
Stack Overflow answerers who are newer and have lower reputation. However, we
leave it as the future work.

\subsubsection{License of Code Snippets} 
\vspace{0.25cm}
\textit{Do Stack Overflow
	answerers aware of the outdated code when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}

\begin{table}
	\centering
	\caption{Inclusion of software license in answer}
	\label{tab:survey_license_include}
	\begin{tabular}{lr}
		\toprule
		Include license? & Amount \\
		\midrule
		No. & 197 \\
		Yes, in code comment &	1 \\
		Yes, in text surrounding the code & 2 \\
		\midrule
		Total & 200 \\
		\bottomrule
	\end{tabular}
\end{table}
